Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 nge.tex
minor fix.

NGE exposes an API for the application  \jhanote{workload management?} layer
to describe workloads (Fig.~\ref{fig:arch-overview}, green squares) and pilots
(Fig.~\ref{fig:arch-overview}, red circles), and to instantiate a PilotManager
and a UnitManager.   The PilotManager submits pilots to Titan's PBS  batch
system via SAGA API (Fig.~\ref{fig:arch-overview}, dash arrow), as done by
PanDA Broker to submit MPI scripts. Once scheduled, the pilot's Agent is
bootstrapped on Titan's MOM node and \jhanote{the Agent's Executors on the}
the Agent's Executors on the worker nodes, and the UnitManager schedules units
to the Agent's Scheduler (Fig.~\ref{fig:arch- overview}, solid arrow). The
Agent's Scheduler schedules the units on one or more Agent's Executor for
execution. The Agent's executors can manage one or more worker nodes,
depending on performance evaluations. The UnitManager and the Agent
communicate via a database that is instantiated on one of Titan's DTN so as to
be reachable by both modules.

>>>>

NGE exposes an API to describe workloads (Fig.~\ref{fig:arch-overview}, green
squares) and pilots (Fig.~\ref{fig:arch-overview}, red circles), and to
instantiate a PilotManager and a UnitManager.   The PilotManager submits
pilots to Titan's PBS  batch system via SAGA API (Fig.~\ref{fig:arch-
overview}, dash arrow), as done by PanDA Broker to submit MPI scripts. Once
scheduled, the pilot's Agent is bootstrapped on Titan's MOM node and
\jhanote{the Agent's Executors on the} the Agent's Executors on the worker
nodes, and the UnitManager schedules units to the Agent's Scheduler
(Fig.~\ref{fig:arch- overview}, solid arrow). The Agent's Scheduler schedules
the units on one or more Agent's Executor for execution. The Agent's executors
can manage one or more worker nodes, depending on performance evaluations. The
UnitManager and the Agent communicate via a database that is instantiated on
one of Titan's DTN so as to be reachable by both modules.
